\class : Problem Set \psetnum

### 2022-05-11 531_stars/pset4/solutions.tex
started first question HW4 stars

\question{\textbf{20.2 - White Dwarf Luminosity}}
\answer{}

>>>>

\question{\textbf{20.2 - White Dwarf Luminosity}}

\question{Part a}
\answer{
    The luminosity of a white dwarf in the slow cooling phase is given by Eq.\ 20.10 in the textbook
    \begin{equation}
        \frac{L}{\unit{L_\odot}} \approx 5.2 \times 10^{10} \frac{M}{\unit{M_\odot}} \mu_{\rm ion}^{-7/5} \qty(\frac{t}{\unit{yr}})^{-7.5}
    \end{equation}
    Since we are comparing white dwarfs with the same cooling age, the only relevant factors are the mass and $\mu_{\rm ion}$ when comparing a H-rich WD to He-rich and C-rich.

    The values of $\mu_{\rm ion}$ for these WDs are $1, 4, 12$ respectively. This means that the relative luminosity of the WDs is
    \begin{equation}
        \frac{L}{L_{\rm H-rich}} = 1 : 0.14 : 0.03
    \end{equation}
    respectively. This shows that H-rich WDs are the brightest for a given cooling age, following my He-rich and then C-rich WDs.

    \todo{Can we assume that the mass is constant?}
}

\question{Part b}
\answer{
    \todo{Unsure, maybe larger ions make cooling happen faster? Why?}
}
